#FOR UNMARKED MOUSE

E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_23450.csv
E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_4hrs_day2_18.2.25/decoded_datalog_21825_41327.csv
E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21925_3636.csv
E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day4_20.2.25/decoded_datalog_22025_45628.csv
E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_0593.csv

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_23450.csv",
"E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_4hrs_day2_18.2.25/decoded_datalog_21825_41327.csv",
"E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21925_3636.csv",
"E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day4_20.2.25/decoded_datalog_22025_45628.csv",
"E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_0593.csv"
)

# Initialize an empty list to store results
all_data <- list()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )
  
  # Filter relevant categories
  data <- data %>% filter(Category %in% c("NP", "RM", "L1", "L2"))
  
  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))
  
  # Count L1, L2, RM per NP within each interval
  interval_counts <- data %>%
    filter(Category != "NP") %>%
    group_by(Interval_ID, Category) %>%
    summarize(Count = n(), .groups = "drop") %>%
    pivot_wider(names_from = Category, values_from = Count, values_fill = 0) %>%
    left_join(
      data %>% filter(Category == "NP") %>% distinct(Interval_ID, Timestamp),
      by = "Interval_ID"
    ) %>%
    arrange(Timestamp)
  
  # Calculate counts per NP
  interval_counts <- interval_counts %>%
    mutate(
      Total_Events = L1 + L2 + RM,
      `L1_per_NP` = L1,
      `L2_per_NP` = L2,
      `RM_per_NP` = RM,
      Day = paste0("Day ", i)  # Assign day label
    )
  
  # Store the processed data
  all_data[[i]] <- interval_counts
}

# Combine all days' data into a single dataframe
combined_data <- bind_rows(all_data)

# Set bin width for histograms
bin_width <- 1  # This keeps bins aligned with RM per NP values

### 1ï¸âƒ£ Stacked Histogram ###
ggplot(combined_data, aes(x = RM_per_NP, fill = Day)) +
  geom_histogram(binwidth = bin_width, alpha = 0.7, position = "stack", color = "black") +
  labs(
    title = "Stacked Histogram of RM per NP Across 5 Days",
    x = "Number of Harvests per Nose Poke",
    y = "Frequency",
    fill = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

### 2ï¸âƒ£ Faceted Histogram ###
ggplot(combined_data, aes(x = RM_per_NP, fill = Day)) +
  geom_histogram(binwidth = bin_width, alpha = 0.7, color = "black") +
  facet_wrap(~Day, ncol = 1) +  # Creates separate rows for each day
  labs(
    title = "Histogram of RM per NP Across 5 Days (Faceted)",
    x = "Number of Harvests per Nose Poke",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 14, face = "bold"), # Make facet labels clearer
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold")
  )

### 3ï¸âƒ£ Density Plot ###
ggplot(combined_data, aes(x = RM_per_NP, color = Day, fill = Day)) +
  geom_density(alpha = 0.3) +
  labs(
    title = "Density Plot of RM per NP Across 5 Days",
    x = "Number of Harvests per Nose Poke",
    y = "Density",
    color = "Day",
    fill = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

```

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)

```

```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_23450.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_4hrs_day2_18.2.25/decoded_datalog_21825_41327.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21925_3636.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day4_20.2.25/decoded_datalog_22025_45628.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_0593.csv"
)

# Initialize an empty list to store results
all_data <- list()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )
  
  # Filter relevant categories
  data <- data %>% filter(Category %in% c("NP", "RM", "L1", "L2"))
  
  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))
  
  # Count L1, L2, RM per NP within each interval
  interval_counts <- data %>%
    filter(Category != "NP") %>%
    group_by(Interval_ID, Category) %>%
    summarize(Count = n(), .groups = "drop") %>%
    pivot_wider(names_from = Category, values_from = Count, values_fill = 0) %>%
    left_join(
      data %>% filter(Category == "NP") %>% distinct(Interval_ID, Timestamp),
      by = "Interval_ID"
    ) %>%
    arrange(Timestamp)
  
  # Calculate counts per NP
  interval_counts <- interval_counts %>%
    mutate(
      Total_Events = L1 + L2 + RM,
      `L1_per_NP` = L1,
      `L2_per_NP` = L2,
      `RM_per_NP` = RM,
      Day = paste0("Day ", i)  # Assign day label
    )
  
  # Store the processed data
  all_data[[i]] <- interval_counts
}

# Combine all days' data into a single dataframe
combined_data <- bind_rows(all_data)

# Set bin width for histograms
bin_width <- 1  # Keeps bins aligned with RM per NP values

### 1ï¸âƒ£ Stacked Histogram ###
ggplot(combined_data, aes(x = RM_per_NP, fill = Day)) +
  geom_histogram(binwidth = bin_width, alpha = 0.7, position = "stack", color = "black") +
  labs(
    title = "Stacked Histogram of RM per NP Across 5 Days",
    x = "Number of Harvests per Nose Poke",
    y = "Frequency",
    fill = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    plot.title = element_text(size = 18, face = "bold"),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 16, face = "bold")
  )

### 2ï¸âƒ£ Faceted Histogram (Improved Readability) ###
ggplot(combined_data, aes(x = RM_per_NP, fill = Day)) +
  geom_histogram(binwidth = bin_width, alpha = 0.7, color = "black") +
  facet_wrap(~Day, ncol = 2, scales = "fixed") +  # Use 2 columns for better spacing
  labs(
    title = "Histogram of RM per NP Across 5 Days (Faceted)",
    x = "Number of Harvests per Nose Poke",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 16, face = "bold"), # Larger facet labels
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    plot.title = element_text(size = 18, face = "bold")
  )

### 3ï¸âƒ£ Density Plot ###
ggplot(combined_data, aes(x = RM_per_NP, color = Day, fill = Day)) +
  geom_density(alpha = 0.3) +
  labs(
    title = "Density Plot of RM per NP Across 5 Days",
    x = "Number of Harvests per Nose Poke",
    y = "Density",
    color = "Day",
    fill = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    plot.title = element_text(size = 18, face = "bold"),
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 16, face = "bold")
  )

```

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_23450.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_4hrs_day2_18.2.25/decoded_datalog_21825_41327.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21925_3636.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day4_20.2.25/decoded_datalog_22025_45628.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_0593.csv"
)

# Initialize lists to store results
all_data <- list()
activity_summary <- data.frame()
reward_summary <- data.frame()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Calculate total experiment duration
  total_duration <- as.numeric(difftime(max(data$Timestamp), min(data$Timestamp), units = "secs"))

  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )
  
  # Compute total active time
  active_time_NP <- sum(data$Category == "NP", na.rm = TRUE)
  active_time_RM <- sum(data$Category == "RM", na.rm = TRUE)
  active_time_L1 <- sum(data$Category == "L1", na.rm = TRUE)
  active_time_L2 <- sum(data$Category == "L2", na.rm = TRUE)
  total_active_time <- active_time_NP + active_time_RM + active_time_L1 + active_time_L2
  total_inactive_time <- total_duration - total_active_time  # Compute inactive time

  # Store activity summary
  activity_summary <- rbind(activity_summary, data.frame(
    Day = paste0("Day ", i),
    Total_Duration = total_duration,
    Active_Time_NP = active_time_NP,
    Active_Time_RM = active_time_RM,
    Active_Time_L1 = active_time_L1,
    Active_Time_L2 = active_time_L2,
    Total_Active_Time = total_active_time,
    Total_Inactive_Time = total_inactive_time
  ))
  
  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))
  
  # Count L1, L2, RM per NP within each interval
  interval_counts <- data %>%
    filter(Category != "NP") %>%
    group_by(Interval_ID, Category) %>%
    summarize(Count = n(), .groups = "drop") %>%
    pivot_wider(names_from = Category, values_from = Count, values_fill = 0) %>%
    left_join(
      data %>% filter(Category == "NP") %>% distinct(Interval_ID, Timestamp),
      by = "Interval_ID"
    ) %>%
    arrange(Timestamp)
  
  # Compute reward accumulation (Exponential Decay)
  reward_trials <- data %>% filter(Category == "RM")  # Get only reward trials
  reward_volume <- numeric(nrow(reward_trials))
  reward_volume[1] <- 80  # Starting reward volume in microliters

  for (j in 2:nrow(reward_trials)) {
    reward_volume[j] <- reward_volume[j - 1] * 0.82  # Exponential decay
  }

  total_reward_consumed <- sum(reward_volume, na.rm = TRUE)  # Compute total reward consumed

  # Store reward summary
  reward_summary <- rbind(reward_summary, data.frame(
    Day = paste0("Day ", i),
    Total_Reward_Consumed = total_reward_consumed
  ))

  # Store processed data
  interval_counts$Day <- paste0("Day ", i)
  all_data[[i]] <- interval_counts
}

# Combine all days' data into a single dataframe
combined_data <- bind_rows(all_data)

# Display Activity Summary Table
print(activity_summary)

# Display Reward Summary Table
print(reward_summary)

# Plot Total Reward Consumed Per Day
ggplot(reward_summary, aes(x = Day, y = Total_Reward_Consumed, fill = Day)) +
  geom_bar(stat = "identity", color = "black") +
  labs(
    title = "Total Reward Consumed Per Day",
    x = "Day",
    y = "Total Reward Consumed (ÂµL)"
  ) +
  theme_minimal()


```
```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_23450.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_4hrs_day2_18.2.25/decoded_datalog_21825_41327.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21925_3636.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day4_20.2.25/decoded_datalog_22025_45628.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_0593.csv"
)

# Initialize lists to store results
all_data <- list()
activity_summary <- data.frame()
reward_summary <- data.frame()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Calculate total experiment duration
  total_duration <- as.numeric(difftime(max(data$Timestamp), min(data$Timestamp), units = "secs"))

  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )
  
  # Compute total active time
  active_time_NP <- sum(data$Category == "NP", na.rm = TRUE)
  active_time_RM <- sum(data$Category == "RM", na.rm = TRUE)
  active_time_L1 <- sum(data$Category == "L1", na.rm = TRUE)
  active_time_L2 <- sum(data$Category == "L2", na.rm = TRUE)
  total_active_time <- active_time_NP + active_time_RM + active_time_L1 + active_time_L2
  total_inactive_time <- total_duration - total_active_time  # Compute inactive time

  # Store activity summary
  activity_summary <- rbind(activity_summary, data.frame(
    Day = paste0("Day ", i),
    Total_Duration = total_duration,
    Active_Time_NP = active_time_NP,
    Active_Time_RM = active_time_RM,
    Active_Time_L1 = active_time_L1,
    Active_Time_L2 = active_time_L2,
    Total_Active_Time = total_active_time,
    Total_Inactive_Time = total_inactive_time
  ))
  
  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))
  
  # Count L1, L2, RM per NP within each interval
  interval_counts <- data %>%
    filter(Category != "NP") %>%
    group_by(Interval_ID, Category) %>%
    summarize(Count = n(), .groups = "drop") %>%
    pivot_wider(names_from = Category, values_from = Count, values_fill = 0) %>%
    left_join(
      data %>% filter(Category == "NP") %>% distinct(Interval_ID, Timestamp),
      by = "Interval_ID"
    ) %>%
    arrange(Timestamp)
  
  # Compute reward accumulation (Exponential Decay) with Reset on Nose Poke
  reward_trials <- data %>% filter(Category == "RM")  # Get only reward trials
  total_reward_consumed <- 0  # Initialize reward counter
  
  if (nrow(reward_trials) > 0) {  # Only process if RM events exist
    reward_volume <- numeric(nrow(reward_trials))
    
    for (j in seq_along(reward_volume)) {
      if (j == 1 || any(data$Category[data$Timestamp == reward_trials$Timestamp[j]] == "NP")) {
        reward_volume[j] <- 80  # Reset on first reward or if a new NP occurs
      } else {
        reward_volume[j] <- reward_volume[j - 1] * 0.82  # Exponential decay
      }
    }
    
    total_reward_consumed <- sum(reward_volume, na.rm = TRUE)  # Compute total reward consumed
  }

  # Store reward summary
  reward_summary <- rbind(reward_summary, data.frame(
    Day = paste0("Day ", i),
    Total_Reward_Consumed = total_reward_consumed
  ))

  # Store processed data
  interval_counts$Day <- paste0("Day ", i)
  all_data[[i]] <- interval_counts
}

# Combine all days' data into a single dataframe
combined_data <- bind_rows(all_data)

# Display Activity Summary Table
print(activity_summary)

# Display Reward Summary Table
print(reward_summary)

# ðŸ”¹ **Plot 1: Total Reward Consumed Per Day**
ggplot(reward_summary, aes(x = Day, y = Total_Reward_Consumed, fill = Day)) +
  geom_bar(stat = "identity", color = "black") +
  labs(
    title = "Total Reward Consumed Per Day",
    x = "Day",
    y = "Total Reward Consumed (ÂµL)"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    plot.title = element_text(size = 18, face = "bold")
  )

# ðŸ”¹ **Plot 2: Faceted Histogram (Improved Readability)**
ggplot(combined_data, aes(x = RM_per_NP, fill = Day)) +
  geom_histogram(binwidth = 1, alpha = 0.7, color = "black") +
  facet_wrap(~Day, ncol = 2, scales = "fixed") +  # Use 2 columns for better spacing
  labs(
    title = "Histogram of RM per NP Across 5 Days (Faceted)",
    x = "Number of Harvests per Nose Poke",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 16, face = "bold"), # Larger facet labels
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    plot.title = element_text(size = 18, face = "bold")
  )

```

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_23450.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_4hrs_day2_18.2.25/decoded_datalog_21825_41327.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21925_3636.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day4_20.2.25/decoded_datalog_22025_45628.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 2 (Unmarked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_0593.csv"
)
# Initialize an empty list to store results
all_data <- list()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )
  
  # Filter relevant categories
  data <- data %>% filter(Category %in% c("NP", "RM", "L1", "L2"))
  
  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))
  
  # Count L1, L2, RM per NP within each interval
  interval_counts <- data %>%
    filter(Category != "NP") %>%
    group_by(Interval_ID, Category) %>%
    summarize(Count = n(), .groups = "drop") %>%
    pivot_wider(names_from = Category, values_from = Count, values_fill = 0) %>%
    left_join(
      data %>% filter(Category == "NP") %>% distinct(Interval_ID, Timestamp),
      by = "Interval_ID"
    ) %>%
    arrange(Timestamp)
  
  # Calculate counts per NP
  interval_counts <- interval_counts %>%
    mutate(
      Total_Events = L1 + L2 + RM,
      `L1_per_NP` = L1,
      `L2_per_NP` = L2,
      `RM_per_NP` = RM,
      Day = paste0("Day ", i)  # Assign day label
    )
  
  # Store the processed data
  all_data[[i]] <- interval_counts
}

# Combine all days' data into a single dataframe
combined_data <- bind_rows(all_data)

### 1. Histogram: Frequency Distribution of RM per NP Across Days ###
ggplot(combined_data, aes(x = RM_per_NP, fill = Day)) +
  geom_histogram(binwidth = 1, position = "dodge", alpha = 0.7, color = "black") +
  labs(
    title = "Histogram of RM per NP Across 5 Days",
    x = "Number of Harvests per Nose Poke",
    y = "Frequency",
    fill = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

### 2. Scatter + Box Plot: Comparing RM per NP Across 5 Days ###
ggplot(combined_data, aes(x = Day, y = RM_per_NP, color = Day)) +
  geom_jitter(size = 3, alpha = 0.6, width = 0.2) +  # Scatter plot for individual data points
  geom_boxplot(alpha = 0.4, outlier.shape = NA) +  # Box plot overlay without outlier points
  labs(
    title = "Comparison of RM per NP Across 5 Days",
    x = "Day",
    y = "Number of Harvests per Nose Poke",
    color = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

```
```

