#FOR MARKED MOUSE

E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_5583.csv
E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_4 hrs_day2_18.2.25/decoded_datalog_21825_01151.csv
E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21825_235740.csv
E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3.5hrs_day4_20.2.25/decoded_datalog_22025_02923.csv
E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_43241.csv


```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_5583.csv",
"E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_4 hrs_day2_18.2.25/decoded_datalog_21825_01151.csv",
"E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21825_235740.csv",
"E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3.5hrs_day4_20.2.25/decoded_datalog_22025_02923.csv",
"E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_43241.csv"
)

# Initialize an empty list to store results
all_data <- list()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i])
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )
  
  # Filter relevant categories
  data <- data %>% filter(Category %in% c("NP", "RM", "L1", "L2"))
  
  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))
  
  # Count L1, L2, RM per NP within each interval
  interval_counts <- data %>%
    filter(Category != "NP") %>%
    group_by(Interval_ID, Category) %>%
    summarize(Count = n(), .groups = "drop") %>%
    pivot_wider(names_from = Category, values_from = Count, values_fill = 0) %>%
    left_join(
      data %>% filter(Category == "NP") %>% distinct(Interval_ID, Timestamp),
      by = "Interval_ID"
    ) %>%
    arrange(Timestamp)
  
  # Calculate counts per NP
  interval_counts <- interval_counts %>%
    mutate(
      Total_Events = L1 + L2 + RM,
      `L1_per_NP` = L1,
      `L2_per_NP` = L2,
      `RM_per_NP` = RM,
      Day = paste0("Day ", i)  # Assign day label
    )
  
  # Store the processed data
  all_data[[i]] <- interval_counts
}

# Combine all days' data into a single dataframe
combined_data <- bind_rows(all_data)

# Reshape data for plotting
plot_data <- combined_data %>%
  select(Timestamp, RM_per_NP, Day) %>%
  pivot_longer(
    cols = c(RM_per_NP),
    names_to = "Category",
    values_to = "Count"
  )

# Plot the data
ggplot(plot_data, aes(x = Timestamp, y = Count, color = Day, group = Day)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    title = "RM per NP Count Trend Across 5 Days",
    x = "Time",
    y = "Number of Harvests per Patch (i.e. RM per NP)",
    color = "Day"
  ) +
  theme_minimal() +
  scale_x_datetime(date_labels = "%H:%M", date_breaks = "1 hour") +  # Adjust x-axis for clarity
  ylim(0, max(plot_data$Count, na.rm = TRUE))  # Ensures consistent y-axis scaling

```
```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_5583.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_4 hrs_day2_18.2.25/decoded_datalog_21825_01151.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21825_235740.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3.5hrs_day4_20.2.25/decoded_datalog_22025_02923.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_43241.csv"
)

# Initialize an empty list to store results
all_data <- list()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )
  
  # Filter relevant categories
  data <- data %>% filter(Category %in% c("NP", "RM", "L1", "L2"))
  
  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))
  
  # Count L1, L2, RM per NP within each interval
  interval_counts <- data %>%
    filter(Category != "NP") %>%
    group_by(Interval_ID, Category) %>%
    summarize(Count = n(), .groups = "drop") %>%
    pivot_wider(names_from = Category, values_from = Count, values_fill = 0) %>%
    left_join(
      data %>% filter(Category == "NP") %>% distinct(Interval_ID, Timestamp),
      by = "Interval_ID"
    ) %>%
    arrange(Timestamp)
  
  # Calculate counts per NP
  interval_counts <- interval_counts %>%
    mutate(
      Total_Events = L1 + L2 + RM,
      `L1_per_NP` = L1,
      `L2_per_NP` = L2,
      `RM_per_NP` = RM,
      Day = paste0("Day ", i)  # Assign day label
    )
  
  # Store the processed data
  all_data[[i]] <- interval_counts
}

# Combine all days' data into a single dataframe
combined_data <- bind_rows(all_data)

# Reshape data for plotting
plot_data <- combined_data %>%
  select(Timestamp, RM_per_NP, Day) %>%
  pivot_longer(
    cols = c(RM_per_NP),
    names_to = "Category",
    values_to = "Count"
  )

# Plot the data
ggplot(plot_data, aes(x = Timestamp, y = Count, color = Day, group = Day)) +
  geom_line(linewidth = 1.2) +  # Fixed deprecated 'size' argument
  geom_point(size = 2) +
  labs(
    title = "RM per NP Count Trend Across 5 Days",
    x = "Time",
    y = "Number of Harvests per Patch (i.e. RM per NP)",
    color = "Day"
  ) +
  theme_minimal() +
  scale_x_datetime(
    date_labels = "%H:%M", date_breaks = "1 hour"  # Ensure readable x-axis labels
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),  # Rotate x-axis labels for clarity
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold"),
    plot.margin = margin(10, 10, 10, 10)  # Adjust margins for better spacing
  ) +
  ylim(0, max(plot_data$Count, na.rm = TRUE))  # Ensures consistent y-axis scaling

```
```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_5583.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_4 hrs_day2_18.2.25/decoded_datalog_21825_01151.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21825_235740.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3.5hrs_day4_20.2.25/decoded_datalog_22025_02923.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_43241.csv"
)

# Initialize an empty list to store results
all_data <- list()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )
  
  # Filter relevant categories
  data <- data %>% filter(Category %in% c("NP", "RM", "L1", "L2"))
  
  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))
  
  # Count L1, L2, RM per NP within each interval
  interval_counts <- data %>%
    filter(Category != "NP") %>%
    group_by(Interval_ID, Category) %>%
    summarize(Count = n(), .groups = "drop") %>%
    pivot_wider(names_from = Category, values_from = Count, values_fill = 0) %>%
    left_join(
      data %>% filter(Category == "NP") %>% distinct(Interval_ID, Timestamp),
      by = "Interval_ID"
    ) %>%
    arrange(Timestamp)
  
  # Calculate counts per NP
  interval_counts <- interval_counts %>%
    mutate(
      Total_Events = L1 + L2 + RM,
      `L1_per_NP` = L1,
      `L2_per_NP` = L2,
      `RM_per_NP` = RM,
      Day = paste0("Day ", i)  # Assign day label
    )
  
  # Store the processed data
  all_data[[i]] <- interval_counts
}

# Combine all days' data into a single dataframe
combined_data <- bind_rows(all_data)

### 1. Histogram: Frequency Distribution of RM per NP Across Days ###
ggplot(combined_data, aes(x = RM_per_NP, fill = Day)) +
  geom_histogram(binwidth = 1, position = "dodge", alpha = 0.7, color = "black") +
  labs(
    title = "Histogram of RM per NP Across 5 Days",
    x = "Number of Harvests per Nose Poke",
    y = "Frequency",
    fill = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

### 2. Scatter + Box Plot: Comparing RM per NP Across 5 Days ###
ggplot(combined_data, aes(x = Day, y = RM_per_NP, color = Day)) +
  geom_jitter(size = 3, alpha = 0.6, width = 0.2) +  # Scatter plot for individual data points
  geom_boxplot(alpha = 0.4, outlier.shape = NA) +  # Box plot overlay without outlier points
  labs(
    title = "Comparison of RM per NP Across 5 Days",
    x = "Day",
    y = "Number of Harvests per Nose Poke",
    color = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

```

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_5583.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_4 hrs_day2_18.2.25/decoded_datalog_21825_01151.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21825_235740.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3.5hrs_day4_20.2.25/decoded_datalog_22025_02923.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_43241.csv"
)

# Initialize an empty list to store results
all_data <- list()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )
  
  # Filter relevant categories
  data <- data %>% filter(Category %in% c("NP", "RM", "L1", "L2"))
  
  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))
  
  # Count L1, L2, RM per NP within each interval
  interval_counts <- data %>%
    filter(Category != "NP") %>%
    group_by(Interval_ID, Category) %>%
    summarize(Count = n(), .groups = "drop") %>%
    pivot_wider(names_from = Category, values_from = Count, values_fill = 0) %>%
    left_join(
      data %>% filter(Category == "NP") %>% distinct(Interval_ID, Timestamp),
      by = "Interval_ID"
    ) %>%
    arrange(Timestamp)
  
  # Calculate counts per NP
  interval_counts <- interval_counts %>%
    mutate(
      Total_Events = L1 + L2 + RM,
      `L1_per_NP` = L1,
      `L2_per_NP` = L2,
      `RM_per_NP` = RM,
      Day = paste0("Day ", i)  # Assign day label
    )
  
  # Store the processed data
  all_data[[i]] <- interval_counts
}

# Combine all days' data into a single dataframe
combined_data <- bind_rows(all_data)

# Set bin width for histograms
bin_width <- 1  # This keeps bins aligned with RM per NP values

### 1ï¸âƒ£ Stacked Histogram ###
ggplot(combined_data, aes(x = RM_per_NP, fill = Day)) +
  geom_histogram(binwidth = bin_width, alpha = 0.7, position = "stack", color = "black") +
  labs(
    title = "Stacked Histogram of RM per NP Across 5 Days",
    x = "Number of Harvests per Nose Poke",
    y = "Frequency",
    fill = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

### 2ï¸âƒ£ Faceted Histogram ###
ggplot(combined_data, aes(x = RM_per_NP, fill = Day)) +
  geom_histogram(binwidth = bin_width, alpha = 0.7, color = "black") +
  facet_wrap(~Day, ncol = 1) +  # Creates separate rows for each day
  labs(
    title = "Histogram of RM per NP Across 5 Days (Faceted)",
    x = "Number of Harvests per Nose Poke",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 14, face = "bold"), # Make facet labels clearer
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold")
  )

### 3ï¸âƒ£ Density Plot ###
ggplot(combined_data, aes(x = RM_per_NP, color = Day, fill = Day)) +
  geom_density(alpha = 0.3) +
  labs(
    title = "Density Plot of RM per NP Across 5 Days",
    x = "Number of Harvests per Nose Poke",
    y = "Density",
    color = "Day",
    fill = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

```
```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_5583.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_4 hrs_day2_18.2.25/decoded_datalog_21825_01151.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21825_235740.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3.5hrs_day4_20.2.25/decoded_datalog_22025_02923.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_43241.csv"
)

# Initialize an empty list to store results
all_data <- list()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )
  
  # Filter relevant categories
  data <- data %>% filter(Category %in% c("NP", "RM", "L1", "L2"))
  
  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))
  
  # Count L1, L2, RM per NP within each interval
  interval_counts <- data %>%
    filter(Category != "NP") %>%
    group_by(Interval_ID, Category) %>%
    summarize(Count = n(), .groups = "drop") %>%
    pivot_wider(names_from = Category, values_from = Count, values_fill = 0) %>%
    left_join(
      data %>% filter(Category == "NP") %>% distinct(Interval_ID, Timestamp),
      by = "Interval_ID"
    ) %>%
    arrange(Timestamp)
  
  # Calculate counts per NP
  interval_counts <- interval_counts %>%
    mutate(
      Total_Events = L1 + L2 + RM,
      `L1_per_NP` = L1,
      `L2_per_NP` = L2,
      `RM_per_NP` = RM,
      Day = paste0("Day ", i)  # Assign day label
    )
  
  # Store the processed data
  all_data[[i]] <- interval_counts
}

# Combine all days' data into a single dataframe
combined_data <- bind_rows(all_data)

# Set bin width for histograms
bin_width <- 1  # Keeps bins aligned with RM per NP values

### 1ï¸âƒ£ Stacked Histogram ###
ggplot(combined_data, aes(x = RM_per_NP, fill = Day)) +
  geom_histogram(binwidth = bin_width, alpha = 0.7, position = "stack", color = "black") +
  labs(
    title = "Stacked Histogram of RM per NP Across 5 Days",
    x = "Number of Harvests per Nose Poke",
    y = "Frequency",
    fill = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

### 2ï¸âƒ£ Faceted Histogram (Fixed Y-Axis + 2 Columns for Better Visibility) ###
ggplot(combined_data, aes(x = RM_per_NP, fill = Day)) +
  geom_histogram(binwidth = bin_width, alpha = 0.7, color = "black") +
  facet_wrap(~Day, ncol = 2, scales = "fixed") +  # 2 columns for better visibility
  labs(
    title = "Histogram of RM per NP Across 5 Days (Faceted)",
    x = "Number of Harvests per Nose Poke",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 14, face = "bold"), # Bigger facet labels
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold")
  )

### 3ï¸âƒ£ Density Plot (Smooth Histogram for Trend Analysis) ###
ggplot(combined_data, aes(x = RM_per_NP, color = Day, fill = Day)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Density Plot of RM per NP Across 5 Days",
    x = "Number of Harvests per Nose Poke",
    y = "Density",
    color = "Day",
    fill = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

```

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_5583.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_4 hrs_day2_18.2.25/decoded_datalog_21825_01151.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21825_235740.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3.5hrs_day4_20.2.25/decoded_datalog_22025_02923.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_43241.csv"
)

# Initialize lists to store results
all_data <- list()
activity_summary <- data.frame()
reward_summary <- data.frame()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Calculate total experiment duration
  total_duration <- as.numeric(difftime(max(data$Timestamp), min(data$Timestamp), units = "secs"))

  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )
  
  # Compute total active time
  active_time_NP <- sum(data$Category == "NP", na.rm = TRUE)
  active_time_RM <- sum(data$Category == "RM", na.rm = TRUE)
  active_time_L1 <- sum(data$Category == "L1", na.rm = TRUE)
  active_time_L2 <- sum(data$Category == "L2", na.rm = TRUE)
  total_active_time <- active_time_NP + active_time_RM + active_time_L1 + active_time_L2
  total_inactive_time <- total_duration - total_active_time  # Compute inactive time

  # Store activity summary
  activity_summary <- rbind(activity_summary, data.frame(
    Day = paste0("Day ", i),
    Total_Duration = total_duration,
    Active_Time_NP = active_time_NP,
    Active_Time_RM = active_time_RM,
    Active_Time_L1 = active_time_L1,
    Active_Time_L2 = active_time_L2,
    Total_Active_Time = total_active_time,
    Total_Inactive_Time = total_inactive_time
  ))
  
  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))
  
  # Count L1, L2, RM per NP within each interval
  interval_counts <- data %>%
    filter(Category != "NP") %>%
    group_by(Interval_ID, Category) %>%
    summarize(Count = n(), .groups = "drop") %>%
    pivot_wider(names_from = Category, values_from = Count, values_fill = 0) %>%
    left_join(
      data %>% filter(Category == "NP") %>% distinct(Interval_ID, Timestamp),
      by = "Interval_ID"
    ) %>%
    arrange(Timestamp)
  
  # Compute reward accumulation (Exponential Decay)
  reward_trials <- data %>% filter(Category == "RM")  # Get only reward trials
  reward_volume <- numeric(nrow(reward_trials))
  reward_volume[1] <- 80  # Starting reward volume in microliters

  for (j in 2:nrow(reward_trials)) {
    reward_volume[j] <- reward_volume[j - 1] * 0.82  # Exponential decay
  }

  total_reward_consumed <- sum(reward_volume, na.rm = TRUE)  # Compute total reward consumed

  # Store reward summary
  reward_summary <- rbind(reward_summary, data.frame(
    Day = paste0("Day ", i),
    Total_Reward_Consumed = total_reward_consumed
  ))

  # Store processed data
  interval_counts$Day <- paste0("Day ", i)
  all_data[[i]] <- interval_counts
}

# Combine all days' data into a single dataframe
combined_data <- bind_rows(all_data)

# Display Activity Summary Table
print(activity_summary)

# Display Reward Summary Table
print(reward_summary)

# Plot Total Reward Consumed Per Day
ggplot(reward_summary, aes(x = Day, y = Total_Reward_Consumed, fill = Day)) +
  geom_bar(stat = "identity", color = "black") +
  labs(
    title = "Total Reward Consumed Per Day",
    x = "Day",
    y = "Total Reward Consumed (ÂµL)"
  ) +
  theme_minimal()


```
```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_5583.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_4 hrs_day2_18.2.25/decoded_datalog_21825_01151.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21825_235740.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3.5hrs_day4_20.2.25/decoded_datalog_22025_02923.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_43241.csv"
)

# Initialize lists to store results
all_data <- list()
reward_accumulation <- list()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )

  # Identify nose pokes
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))

  # Filter only reward trials
  reward_trials <- data %>% filter(Category == "RM")  
  reward_volume <- numeric(nrow(reward_trials))

  # Track reward accumulation per NP
  cumulative_reward <- 0
  reset_index <- 1
  reward_tracking <- data.frame()

  for (j in seq_along(reward_volume)) {
    if (j == 1 || any(data$Category[data$Timestamp == reward_trials$Timestamp[j]] == "NP")) {
      # Reset at each new NP
      reward_volume[j] <- 80  
      cumulative_reward <- 80
      reset_index <- j
    } else {
      # Apply decay within a single NP cycle
      reward_volume[j] <- reward_volume[j - 1] * 0.82
      cumulative_reward <- cumulative_reward + reward_volume[j]
    }

    # Store cumulative reward per NP
    reward_tracking <- rbind(reward_tracking, data.frame(
      Timestamp = reward_trials$Timestamp[j],
      Interval_ID = reward_trials$Interval_ID[j],
      Cumulative_Reward = cumulative_reward,
      Day = paste0("Day ", i)
    ))
  }

  reward_accumulation[[i]] <- reward_tracking
}

# Combine data for plotting
reward_accumulation_data <- bind_rows(reward_accumulation)

# Plot Reward Accumulation per NP Before Reset
ggplot(reward_accumulation_data, aes(x = Interval_ID, y = Cumulative_Reward, color = Day)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    title = "Reward Accumulation Before Reset (Per Nose Poke)",
    x = "Nose Poke Interval",
    y = "Cumulative Reward (ÂµL)",
    color = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

```
```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_5583.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_4 hrs_day2_18.2.25/decoded_datalog_21825_01151.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21825_235740.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3.5hrs_day4_20.2.25/decoded_datalog_22025_02923.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_43241.csv"
)

# Initialize lists to store results
all_data <- list()
activity_summary <- data.frame()
reward_summary <- data.frame()
reward_accumulation <- list()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )

  # Compute total experiment duration
  total_duration <- as.numeric(difftime(max(data$Timestamp), min(data$Timestamp), units = "secs"))

  # Compute total active time
  active_time_NP <- sum(data$Category == "NP", na.rm = TRUE)
  active_time_RM <- sum(data$Category == "RM", na.rm = TRUE)
  active_time_L1 <- sum(data$Category == "L1", na.rm = TRUE)
  active_time_L2 <- sum(data$Category == "L2", na.rm = TRUE)
  total_active_time <- active_time_NP + active_time_RM + active_time_L1 + active_time_L2
  total_inactive_time <- total_duration - total_active_time  # Compute inactive time

  # Store activity summary
  activity_summary <- rbind(activity_summary, data.frame(
    Day = paste0("Day ", i),
    Total_Duration = total_duration,
    Active_Time_NP = active_time_NP,
    Active_Time_RM = active_time_RM,
    Active_Time_L1 = active_time_L1,
    Active_Time_L2 = active_time_L2,
    Total_Active_Time = total_active_time,
    Total_Inactive_Time = total_inactive_time
  ))

  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))

  # Compute reward accumulation (Exponential Decay) with Reset on Nose Poke
  reward_trials <- data %>% filter(Category == "RM")  
  reward_volume <- numeric(nrow(reward_trials))
  cumulative_reward <- 0
  reward_tracking <- data.frame()

  for (j in seq_along(reward_volume)) {
    if (j == 1 || any(data$Category[data$Timestamp == reward_trials$Timestamp[j]] == "NP")) {
      reward_volume[j] <- 80  # Reset on first reward or if a new NP occurs
      cumulative_reward <- 80
    } else {
      reward_volume[j] <- reward_volume[j - 1] * 0.82  # Apply decay
      cumulative_reward <- cumulative_reward + reward_volume[j]
    }

    # Store cumulative reward per NP
    reward_tracking <- rbind(reward_tracking, data.frame(
      Timestamp = reward_trials$Timestamp[j],
      Interval_ID = reward_trials$Interval_ID[j],
      Cumulative_Reward = cumulative_reward,
      Day = paste0("Day ", i)
    ))
  }

  reward_accumulation[[i]] <- reward_tracking

  # Compute total reward consumed
  total_reward_consumed <- sum(reward_volume, na.rm = TRUE)

  # Store reward summary
  reward_summary <- rbind(reward_summary, data.frame(
    Day = paste0("Day ", i),
    Total_Reward_Consumed = total_reward_consumed
  ))
}

# Combine data for plotting
reward_accumulation_data <- bind_rows(reward_accumulation)

# Ensure all days exist in the dataset
all_days <- paste0("Day ", 1:5)
missing_days <- setdiff(all_days, unique(reward_accumulation_data$Day))

# If any days are missing, add a dummy zero-entry to make them appear
for (day in missing_days) {
  reward_accumulation_data <- rbind(reward_accumulation_data, 
    data.frame(Timestamp = NA, Interval_ID = 1, Cumulative_Reward = 0, Day = day))
}

# Display Activity Summary Table
print(activity_summary)

# Display Reward Summary Table
print(reward_summary)

# ðŸ”¹ **Plot 1: Total Reward Consumed Per Day**
ggplot(reward_summary, aes(x = Day, y = Total_Reward_Consumed, fill = Day)) +
  geom_bar(stat = "identity", color = "black") +
  labs(
    title = "Total Reward Consumed Per Day",
    x = "Day",
    y = "Total Reward Consumed (ÂµL)"
  ) +
  theme_minimal()

# ðŸ”¹ **Plot 2: Reward Accumulation Per NP Before Reset**
ggplot(reward_accumulation_data, aes(x = Interval_ID, y = Cumulative_Reward, color = Day)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    title = "Reward Accumulation Before Reset (Per Nose Poke)",
    x = "Nose Poke Interval",
    y = "Cumulative Reward (ÂµL)",
    color = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

```
```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
```


```{r}
# Define file paths
file_paths <- c(
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day1_17.2.25/decoded_datalog_21725_5583.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_4 hrs_day2_18.2.25/decoded_datalog_21825_01151.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3hrs_day3_19.2.25/decoded_datalog_21825_235740.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week 5_3.5hrs_day4_20.2.25/decoded_datalog_22025_02923.csv",
  "E:/Shrutika-Operant_Chamber-Training Data/Mouse 1 (Marked)/Training CSVs/week5_3hrs_day5_21.2.25/decoded_datalog_22125_43241.csv"
)

# Initialize lists to store results
all_data <- list()
activity_summary <- data.frame()
reward_summary <- data.frame()
reward_accumulation <- list()

# Loop over file paths to process each day's data
for (i in seq_along(file_paths)) {
  data <- read_csv(file_paths[i], show_col_types = FALSE)  # Suppress column type messages
  
  # Combine 'HR', 'M', 'D', and 'Y' into a datetime object
  data$Timestamp <- as.POSIXct(
    paste(data$Y, data$M, data$D, data$HR, data$MIN, data$SEC),
    format = "%Y %m %d %H %M %S"
  )
  
  # Assign categories
  data$Category <- case_when(
    data$Decoded_NosePoke == "NP" ~ "NP",
    data$Decoded_Reward == "RM" ~ "RM",
    data$Decoded_Lever_1 == "L1" ~ "L1",
    data$Decoded_Lever_2 == "L2" ~ "L2",
    TRUE ~ NA_character_
  )

  # Compute total experiment duration
  total_duration <- as.numeric(difftime(max(data$Timestamp), min(data$Timestamp), units = "secs"))

  # Compute total active time
  active_time_NP <- sum(data$Category == "NP", na.rm = TRUE)
  active_time_RM <- sum(data$Category == "RM", na.rm = TRUE)
  active_time_L1 <- sum(data$Category == "L1", na.rm = TRUE)
  active_time_L2 <- sum(data$Category == "L2", na.rm = TRUE)
  total_active_time <- active_time_NP + active_time_RM + active_time_L1 + active_time_L2
  total_inactive_time <- total_duration - total_active_time  # Compute inactive time

  # Store activity summary
  activity_summary <- rbind(activity_summary, data.frame(
    Day = paste0("Day ", i),
    Total_Duration = total_duration,
    Active_Time_NP = active_time_NP,
    Active_Time_RM = active_time_RM,
    Active_Time_L1 = active_time_L1,
    Active_Time_L2 = active_time_L2,
    Total_Active_Time = total_active_time,
    Total_Inactive_Time = total_inactive_time
  ))

  # Identify intervals between consecutive NPs
  data <- data %>%
    mutate(Interval_ID = cumsum(Category == "NP"))

  # Compute reward accumulation (Exponential Decay) with Reset on Nose Poke
  reward_trials <- data %>% filter(Category == "RM")  
  reward_volume <- numeric(nrow(reward_trials))
  cumulative_reward_per_session <- 0  # Track total session reward
  reward_tracking <- data.frame()

  for (j in seq_along(reward_volume)) {
    if (j == 1 || any(data$Category[data$Timestamp == reward_trials$Timestamp[j]] == "NP")) {
      reward_volume[j] <- 80  # Reset on first reward or new NP
    } else {
      reward_volume[j] <- reward_volume[j - 1] * 0.82  # Apply decay
    }
    
    cumulative_reward_per_session <- cumulative_reward_per_session + reward_volume[j]  # Accumulate reward

    # Store cumulative reward per NP
    reward_tracking <- rbind(reward_tracking, data.frame(
      Timestamp = reward_trials$Timestamp[j],
      Interval_ID = reward_trials$Interval_ID[j],
      Cumulative_Reward = cumulative_reward_per_session,
      Day = paste0("Day ", i)
    ))
  }

  reward_accumulation[[i]] <- reward_tracking

  # Store total reward consumed correctly
  total_reward_consumed <- cumulative_reward_per_session

  reward_summary <- rbind(reward_summary, data.frame(
    Day = paste0("Day ", i),
    Total_Reward_Consumed = total_reward_consumed
  ))
}

# Combine data for plotting
reward_accumulation_data <- bind_rows(reward_accumulation)

# Ensure all days exist in the dataset before plotting
all_days <- paste0("Day ", 1:5)
missing_days <- setdiff(all_days, unique(reward_accumulation_data$Day))

# Add a dummy entry if a day is missing to ensure it appears in the plot
for (day in missing_days) {
  reward_accumulation_data <- rbind(reward_accumulation_data, 
    data.frame(Timestamp = NA, Interval_ID = 1, Cumulative_Reward = 0, Day = day))
}

# Display Activity Summary Table
print(activity_summary)

# Display Reward Summary Table
print(reward_summary)

# ðŸ”¹ **Plot 1: Total Reward Consumed Per Day**
ggplot(reward_summary, aes(x = Day, y = Total_Reward_Consumed, fill = Day)) +
  geom_bar(stat = "identity", color = "black") +
  labs(
    title = "Total Reward Consumed Per Day",
    x = "Day",
    y = "Total Reward Consumed (ÂµL)"
  ) +
  theme_minimal()

# ðŸ”¹ **Plot 2: Reward Accumulation Per NP Before Reset**
ggplot(reward_accumulation_data, aes(x = Interval_ID, y = Cumulative_Reward, color = Day)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    title = "Reward Accumulation Before Reset (Per Nose Poke)",
    x = "Nose Poke Interval",
    y = "Cumulative Reward (ÂµL)",
    color = "Day"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 16, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold")
  )

```

